---
title: "Data_Transformation"
author: "Chenrui_Xiao"
date: "2024-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Define Data Transformation Function

A Data Transformation Function is defined below. It applies logarithmic transformation to the second column in a dataset.

```{r function_definition}

ln_trans <- function(data) {
  #transform second column to ln_data
  data[2] <- log(data[2])
  return(data)
}

```

## Function Test

We can test the function using prssure, a built-in R dataset. It is a dataset that shows the relationship between pressure and temperature.

First, we plot the dataset.

```{r prssure}
plot(pressure)

```

Looks like it is suitable for ln_trans!
Now let's try the function and see how the plot changes.

```{r function test}
ln_pressure <- ln_trans(pressure)
plot(ln_pressure)
```

## Define New Data Transformation Function

A New Data Transformation Function is defined below. It applies square root transformation to the second column in a dataset.

```{r new function_definition}

sqrt_trans <- function(data) {
  #transform second column to ln_data
  data[2] <- sqrt(data[2])
  return(data)
}

```

We can also test the new function with the pressure dataset.

```{r new function test}
sqrt_pressure <- sqrt_trans(pressure)
plot(sqrt_pressure)
```
